---
title: "P8105_hw5_tj2383"
author: "Tanvi Jain"
date: "11/5/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
set.seed(1)
```

##Problem 1

In this code chunk I read in the data and created the dataframe along with the variables for control/experiment arm, subject ID, and value. Then I unnested the `value` variable to separate out the weeks and I aggregated across weeks to tidy the data. Lastly, I renamed the values under the `arm` variable and specified them as Control or Experiment. 
```{r}
data = list.files(path = "./data", full.names = TRUE)

longitudinal_data =
  tibble(
    arm = str_detect(data, "con"),
    subject_id = str_extract(data, "\\d+(?=.csv)"),
    value = map(data, read_csv)
  )

longitudinal_data_clean = longitudinal_data %>% 
  unnest() %>% 
  gather(key = "week", week_1:week_8, value = "value") %>% 
  mutate(week = as.numeric(str_extract(week, "\\d")))

longitudinal_data_clean$arm = as.character(longitudinal_data_clean$arm)
longitudinal_data_clean$arm[longitudinal_data_clean$arm == "TRUE"] = "Control"
longitudinal_data_clean$arm[longitudinal_data_clean$arm == "FALSE"] = "Experiment"
```

The following spaghetti plot shows observations on each subject over time according to the control or experiment arm.
```{r}
longitudinal_data_clean %>% 
  ggplot(aes(x = week, y = value, color = subject_id)) +
    geom_line() +
    facet_grid(~arm) +
    viridis::scale_color_viridis(
      discrete = TRUE,
      name = "subject_id"
    ) +
    labs(
      x = "Week",
      y = "Value",
      title = "Observations for each subject over time and by arm"
    ) +
    theme_bw()
```
From this plot it is clear that the values for those in the experiment arm fluctuate but are overall increasing over time. However, for the control arm we see that the values fluctuate but remain low over time.


##Problem 2

Reading in the homicide data.
```{r}
homicide_data = read.csv("./data/homicide-data.csv")
```

