---
title: "P8105_hw5_tj2383"
author: "Tanvi Jain"
date: "11/5/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
set.seed(1)
```

##Problem 1

In this code chunk I read in the data and created a dataset along with the variables for control/experiment arm, subject ID, and value. Then I unnested the `value` variable to separate out the weeks and I aggregated across weeks to tidy the data. Lastly, I renamed the values under the `arm` variable and specified them as Control or Experiment. 
```{r}
data = list.files(path = "./data", full.names = TRUE)

longitudinal_data =
  tibble(
    arm = str_detect(data, "con"),
    subject_id = str_extract(data, "\\d+(?=.csv)"),
    value = map(data, read_csv)
  )

longitudinal_data_clean = longitudinal_data %>% 
  unnest() %>% 
  gather(key = "week", week_1:week_8, value = "value") %>% 
  mutate(week = as.numeric(str_extract(week, "\\d")))

longitudinal_data_clean$arm = as.character(longitudinal_data_clean$arm)
longitudinal_data_clean$arm[longitudinal_data_clean$arm == "TRUE"] = "Control"
longitudinal_data_clean$arm[longitudinal_data_clean$arm == "FALSE"] = "Experiment"
```

The following spaghetti plot shows observations on each subject over time according to the control or experiment arm.
```{r}
longitudinal_data_clean %>% 
  ggplot(aes(x = week, y = value, color = subject_id)) +
    geom_line() +
    facet_grid(~arm) +
    viridis::scale_color_viridis(
      discrete = TRUE,
      name = "subject_id"
    ) +
    labs(
      x = "Week",
      y = "Value",
      title = "Observations for each subject over time and by arm"
    ) +
    theme_bw()
```
From this plot it is clear that the values for those in the experiment arm fluctuate but are overall increasing over time. However, for the control arm we see that the values fluctuate but remain low over time.


##Problem 2

Reading in the homicide data and describing the overall dataset.
```{r}
homicide_data = read.csv("./data/homicide-data.csv")

homicide_data %>% 
  nrow()

homicide_data %>% 
  ncol()

homicide_data %>% 
  select(victim_age) %>% 
  head(1)

homicide_data %>% 
  select(victim_sex) %>% 
  head(1)

homicide_data %>% 
  select(victim_first, victim_last) %>% 
  head(1)

homicide_data %>% 
  select(city, state) %>% 
  head(1)

homicide_data %>% 
  select(disposition) %>% 
  head(1)
```
This dataset contains information on homicides from 50 cities across the United States over a decade. The Washington Post has identified the places where murder is common but arrests are rare. The dataset contains `r homicide_data %>% nrow() ` reports on homicides and `r homicide_data %>% ncol() ` variables. The key variables include victim's last name (`victim_last`), victim's first name (`victim_first`), race of the victim (`victim_race`), victim's age (`victim_age`), victim's sex (`victim_sex`), `city` of homicide, `state` of homicide, and the `disposition`. The following is an example of this data: This victim is a `r homicide_data %>% select(victim_sex) %>% head(1)` of `r homicide_data %>% select(victim_age) %>% head(1) ` age and his name is `r homicide_data %>% select(victim_first, victim_last) %>% head(1) `. The homicide occurred in `r homicide_data %>% select(city, state) %>% head(1) ` and the status of the case is `r homicide_data %>% select(disposition) %>% head(1)`.


In this code chunk, I create a `city_state` variable. Then I created a new dataset called total_homicides that summarizes within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).
```{r}
homicide_data_combined = 
  homicide_data %>% 
  mutate(city_state = paste(city, state, sep = ", ")) %>% 
  select(-city, -state)

total_homicides = 
  homicide_data_combined %>% 
  group_by(city_state) %>% 
  summarize(total_homicides = n(), unsolved_homicides = sum(disposition == "Closed without arrest" | disposition == "Open/No arrest"))
```

In this code chunk I calculate the proportion of homicides that are unsolved for Baltimore.
```{r}
baltimore_homicides =
  total_homicides %>% 
  filter(city_state == "Baltimore, MD")
  
prop = 
  prop.test(x = baltimore_homicides$unsolved_homicides,
            n = baltimore_homicides$total_homicides) %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high)
prop$estimate
prop$conf.low
prop$conf.high
```
The estimated proportion of unsolved cases in Baltimore is `r prop$estimate` and the 95% confidence interval is from `r prop$conf.low` to `r prop$conf.high`.


In this code chunk I created a dataset with the estimated proportion of unsolved cases and corresponding 95% CIs for each city.
```{r}
prop_unsolved = function(x, y) {
   est_prop = 
     prop.test(x = x, n = y) %>% 
     broom::tidy() %>% 
     select(estimate, conf.low, conf.high)
}

homicides =
  map2(.x = total_homicides$unsolved_homicides, 
       .y = total_homicides$total_homicides, 
       ~prop_unsolved(.x, .y)) %>% 
  bind_rows() %>% 
  bind_cols(total_homicides) %>% 
  mutate(conf_low = conf.low,
         conf_high = conf.high) %>% 
  select(city_state, total_homicides, unsolved_homicides, estimate, conf_low, conf_high)

```


The following is a plot of the estimated proportions of unsolved cases with their respective CIs for each city.
```{r}
homicides %>% 
  mutate(city_state = forcats::fct_inorder(city_state)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf_low, ymax = conf_high)) +
  labs(
    x = "city_state",
    y = "estimated proportions of unsolved cases",
    title = "Estimated proportion of unsolved cases in the U.S."
  ) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, size = 7))
```






