---
title: "P8105_hw5_tj2383"
author: "Tanvi Jain"
date: "11/5/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
set.seed(1)
```

##Problem 1

In this code chunk I read in the data and created the dataframe along with the variables for control/experiment arm, subject ID, and value. Then I unnested the `value` variable to separate out the weeks and I aggregated across weeks to tidy the data. Lastly, I renamed the values under the `arm` variable and specified them as Control or Experiment. 
```{r}
data = list.files(path = "./data", full.names = TRUE)

longitudinal_data =
  tibble(
    arm = str_detect(data, "con"),
    subject_id = str_extract(data, "\\d+(?=.csv)"),
    value = map(data, read_csv)
  )

longitudinal_data_clean = longitudinal_data %>% 
  unnest() %>% 
  gather(key = "week", week_1:week_8, value = "value") %>% 
  mutate(week = as.numeric(str_extract(week, "\\d")))

longitudinal_data_clean$arm = as.character(longitudinal_data_clean$arm)
longitudinal_data_clean$arm[longitudinal_data_clean$arm == "TRUE"] = "Control"
longitudinal_data_clean$arm[longitudinal_data_clean$arm == "FALSE"] = "Experiment"
```

The following spaghetti plot shows observations on each subject over time according to the control or experiment arm.
```{r}
longitudinal_data_clean %>% 
  ggplot(aes(x = week, y = value, color = subject_id)) +
    geom_line() +
    facet_grid(~arm) +
    viridis::scale_color_viridis(
      discrete = TRUE,
      name = "subject_id"
    ) +
    labs(
      x = "Week",
      y = "Value",
      title = "Observations for each subject over time and by arm"
    ) +
    theme_bw()
```
From this plot it is clear that the values for those in the experiment arm fluctuate but are overall increasing over time. However, for the control arm we see that the values fluctuate but remain low over time.


##Problem 2

Reading in the homicide data and calculating some descriptive statistics to describe the dataset.
```{r}
homicide_data = read.csv("./data/homicide-data.csv")

homicide_data %>% 
  nrow()

homicide_data %>% 
  ncol()

homicide_data %>% 
  select(victim_age) %>% 
  head(1)

homicide_data %>% 
  select(victim_sex) %>% 
  head(1)

homicide_data %>% 
  select(victim_first, victim_last) %>% 
  head(1)

homicide_data %>% 
  select(city, state) %>% 
  head(1)

homicide_data %>% 
  select(disposition) %>% 
  head(1)
```
This dataset contains information on homicides from 50 cities across the United States over a decade. The Washington Post has identified the places where murder is common but arrests are rare. The dataset contains `r homicide_data %>% nrow() ` reports on homicides and `r homicide_data %>% ncol() ` variables. The key variables include victim's last name (`victim_last`), victim's first name (`victim_first`), race of the victim (`victim_race`), victim's age (`victim_age`), victim's sex (`victim_sex`), `city` of homicide, `state` of homicide, and the `disposition`. The following is an example of this data: This victim is a `r homicide_data %>% select(victim_sex) %>% head(1)` of `r homicide_data %>% select(victim_age) %>% head(1) ` age and his name is `r homicide_data %>% select(victim_first, victim_last) %>% head(1) `. The homicide occurred in `r homicide_data %>% select(city, state) %>% head(1) ` and the status of the case is `r homicide_data %>% select(disposition) %>% head(1)`.


In this code chunk, I create a city_state variable. And then I summarized within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).
```{r}
homicide_data_combined = 
  homicide_data %>% 
  mutate(city_state = paste(city, state, sep = ", ")) %>% 
  select(-city, -state)
```





